Analysis Stand Features 

### 2017-05-11 analysis/analysis_stand_features.Rmd
update aov analysis

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
```

@@

@@

@@

# Topographic data
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

topo <- topo %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF))

@@

Conclusiones_Taller_EME_SN_borrador_para_devolucion.doc

>>>>

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

@@

# General Variables 
```{r}
general_var <- ft %>% group_by(loc, site) %>% count()

general_var %>% kable()
```

@@

coords_sites %>% kable()
```

# Topographic data
## Data summary 
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

topo <- topo %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF)) %>% 
  mutate(site = as.factor(site),
         loc = as.factor(loc),
         elevF = as.factor(elevF))

# Another way to obtain summary values 
variables <- c('mde','slope','aspect')
auxdf <- data.frame()

for (i in variables){ 
aux <- topo %>% 
  dplyr::group_by(site) %>% 
  summarise_each_(funs(mean, sd, se=sd(.)/sqrt(n())), i) %>% mutate(variable=i)

auxdf <- rbind(auxdf, aux) }
```

## ANOVAs 
### Elevation
```{r}
mivariable <- 'mde'

# Model 
myformula <- as.formula(paste0(mivariable, " ~ site"))
mymodel <- aov(myformula, data=topo)

auxdf %>% 
  dplyr::filter(variable==mivariable) %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

## Summary model 
tm <- broom::tidy(mymodel)

# See http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1) 
pander(tm, round=5,caption = "ANOVA table", missing = '', 
       emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))

## Multiple comparison 
tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

# Convert comparisons into letters 
df_letter <- fortify(cld(tuk)) %>%
  transmute(site = as.factor(lhs),
         tukey = letters) %>%
  mutate(variable = mivariable)

aux_name <- paste0('df_tuk_', mivariable)
assign(aux_name, df_letter)

# Get table 
mymult <- as.data.frame(table_glht(tuk))
pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))
```

### Slope
```{r}
mivariable <- 'slope'

# Model 
myformula <- as.formula(paste0(mivariable, " ~ site"))
mymodel <- aov(myformula, data=topo)

auxdf %>% 
  dplyr::filter(variable==mivariable) %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

## Summary model 
tm <- broom::tidy(mymodel)

# See http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1) 
pander(tm, round=5,caption = "ANOVA table", missing = '', 
       emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))

## Multiple comparison 
tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

# Convert comparisons into letters 
df_letter <- fortify(cld(tuk)) %>%
  transmute(site = as.factor(lhs),
         tukey = letters) %>%
  mutate(variable = mivariable)

aux_name <- paste0('df_tuk_', mivariable)
assign(aux_name, df_letter)

# Get table 
mymult <- as.data.frame(table_glht(tuk))
a <- pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))
```

compe <- compe %>% 
  mutate(name = id_focal) %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF)) %>% 
  mutate(site = as.factor(site),
         loc = as.factor(loc),
         elevF = as.factor(elevF))

@@

```{r}
xxx <- function(df, mivariable, mygroup){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest
  # mygroup: factor variable

  # Model formulation
  myformula <- as.formula(paste0(mivariable, " ~ ", mygroup))

  # AOV 
  mymodel <- aov(myformula, data=df)

  # Summary AOV (broom style)
  tm <- broom::tidy(mymodel)

  # Multiple comparison 
  tuk <- glht(mymodel, linfct = mcp(mygroup = "Tukey"))

  # Convert comparisons into letters 
  df_letter <- fortify(cld(tuk)) %>% 
    transmute(site = as.factor(lhs),
         tukey = letters) %>%
    mutate(variable = mivariable)

  aux_name <- paste0('df_tuk_', mivariable)
  assign(aux_name, df_letter)

  mymult <- as.data.frame(table_glht(tuk))

  mymodel
  tm
  aux_name
  mymult
}

 args <- list("Tukey")
           names(args) <- X
           cmp <- do.call(mcp, args)
           glht(fm1, linfct = cmp)

df <- topo
mivariable <- 'slope'
mygroup <- 'site'

ala <- xxx(df=topo, mivariable='slope', mygroup='site' )

auxdf %>% 
  dplyr::filter(variable==mivariable) %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

# See http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1) 
pander(tm, round=5,caption = "ANOVA table", missing = '', 
       emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))

## Multiple comparison 
tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

# Convert comparisons into letters 
df_letter <- fortify(cld(tuk)) %>%
  transmute(site = as.factor(lhs),
         tukey = letters) %>%
  mutate(variable = mivariable)

aux_name <- paste0('df_tuk_', mivariable)
assign(aux_name, df_letter)

# Get table 
mymult <- as.data.frame(table_glht(tuk))
a <- pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))

@@
